---
title: "Software"
toc: true
comments: false
---

```{r}
#| label: startup
#| include: false
library(tidyverse)
library(lubridate)
library(pkgsearch)
library(DT)
library(cranlogs)
library(gh)
```

I've written a few [R packages](https://r-pkgs.org/) over the years and have contributed to many others. 

The CRAN sections below enumerate packages on [CRAN](https://cran.r-project.org/). Download statistics are from the Posit mirror of CRAN and are current as of `r today()`, star statistics were generated at the same time.

```{r}
#| label: find-packages
#| include: false

check_authors <- function(x) {
 if (any(names(x) == "Authors@R")) {
  author_detail <- eval(parse(text = x$`Authors@R`))
 } else {
  author_detail <- x$Author
 }
 any(grepl("Simon.*Couch", author_detail))
}

pick_url <- function(x, pkg) {
 if (is.na(x)) {
  return(cli::format_inline("https://CRAN.R-project.org/package={pkg}"))
 }
 x = gsub("\n", "", x)
 x <- strsplit(x, split = ",")[[1]]
 pkgdown <- grepl("(\\.io)|(\\.org)", x)
 if (any(pkgdown)) {
  x <- x[pkgdown]
 }
 x[1]
}

couch_pkgs <-
 advanced_search(Author = "couch", size = 100) %>%
 as_tibble() %>%
 mutate(its_a_me = map_lgl(package_data,check_authors)) %>%
 filter(its_a_me) %>%
 select(package, title, maintainer = maintainer_name, 
        `reverse dependencies` = revdeps, url) %>%
 mutate(
  url = map2_chr(url, package, pick_url),
  topic = glue::glue("<a href='{url}' target='_blank'>{package}</a>")
 ) %>% 
 mutate(package = factor(package)) %>%
 arrange(package)

downloads <-
 cran_downloads(couch_pkgs$package, from = ymd("2005-01-01"), to = today()) %>%
 summarize(downloads = sum(count), .by = c(package))

couch_pkgs <- 
 full_join(couch_pkgs, downloads, by = "package") %>%
 mutate(downloads = format(downloads, big.mark = ","))
```

<br>

## CRAN Packages Maintained By Me

```{r}
#| label: simon
#| echo: false
couch_pkgs %>% 
 filter(maintainer %in% c("Simon Couch", "Simon P. Couch")) %>% 
 select(package = topic, title, downloads) %>% 
 datatable(rownames = FALSE,
           class = 'cell-border stripe',
           filter = 'top',
           escape = FALSE,
           options = list(pageLength = 100, lengthChange = FALSE))
```


<br>

## CRAN Packages Maintained By Others

These packages are those that I have either originally maintained, significantly contributed to directly, or my code was included enough to be listed as a co-author:

```{r}
#| label: others
#| echo: false
couch_pkgs %>% 
 filter(!maintainer %in% c("Simon Couch", "Simon P. Couch")) %>% 
 select(package = topic, title, maintainer, downloads) %>% 
 datatable(rownames = FALSE,
           class = 'cell-border stripe',
           filter = 'top',
           escape = FALSE,
           options = list(pageLength = 100, lengthChange = FALSE))
```

I've also worked on many [tidymodels packages](https://github.com/tidymodels) that I'm not listed as an author on.


<br>

## GitHub-Only Packages

I've also prototyped some other packages that haven't made it to CRAN.

```{r}
#| label: github-packages
#| echo: false
repos <- gh("/users/simonpcouch/repos", .limit = 100) %>%
  tibble::tibble(
    name = map_chr(., "name"),
    description = map_chr(., "description", .default = NA_character_),
    html_url = map_chr(., "html_url"),
    updated_at = map_chr(., "updated_at"),
    language = map_chr(., "language", .default = NA_character_),
    fork = map_lgl(., "fork")
  ) %>%
  filter(!fork)

has_description <- function(repo) {
  tryCatch({
    contents <- gh("/repos/simonpcouch/{repo}/contents", repo = repo)
    any(map_chr(contents, "name") == "DESCRIPTION")
  }, error = function(e) {
    FALSE
  })
}

github_only_pkgs <- repos %>%
  mutate(has_desc = map_lgl(name, has_description)) %>%
  filter(has_desc) %>%
  filter(!name %in% couch_pkgs$package) %>%
  mutate(
    url = html_url,
    package = glue::glue("<a href='{url}' target='_blank'>{name}</a>"),
    stars = map_int(name, ~{
      tryCatch({
        repo_data <- gh("/repos/simonpcouch/{repo}", repo = .x)
        as.integer(repo_data$stargazers_count)
      }, error = function(e) {
        0L
      })
    })
  ) %>%
  arrange(desc(stars), name)

github_only_pkgs %>%
  select(package, description, stars, updated = updated_at) %>%
  filter(!grepl("slides", description)) %>%
  mutate(updated = as.Date(updated)) %>%
  filter(updated > "2021-12-31") %>%
  filter(!is.na(description)) %>%
  arrange(desc(updated)) %>%
  datatable(rownames = FALSE,
            class = 'cell-border stripe',
            filter = 'top',
            escape = FALSE,
            options = list(pageLength = 100, lengthChange = FALSE))
```

----

The source code from this page was adapted from [Max Kuhn's website](https://github.com/topepo/max-kuhn.org/blob/195694ce465a1773d583877fdab4a01f16bc6c0d/software.qmd).
